%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Speaker Agreement
% LaTeX Template
%
% This template has been downloaded from:
% https://github.com/anjuan/speaker-agreement
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,12pt]{article} % The default font size is 12pt on A4 paper, change to 'usletter' for US Letter paper and adjust margins in structure.tex

\input{structure.tex} % Input the structure.tex file which specifies the document layout and style

%----------------------------------------------------------------------------------------
%	DYNAMIC CONTRACT INFORMATION
%----------------------------------------------------------------------------------------

% Your full name and company name
\newcommand{\YourName}{[YourName]}
\newcommand{\CompanyName}{[CompanyName}

% Your full speaker fee in '$#,###' format.
\newcommand{\FullFee}{[FullFee]}

% Half of your speaker fee in '$#,###' format.
\newcommand{\HalfFee}{[HalfFee]}

% Your talk title
\newcommand{\TalkTitle}{[TalkTitle]}

% Your address
\newcommand{\AddressLineOne}{[YourAddress1]}
\newcommand{\AddressLineTwo}{[YourAddress2]}

% Your email address
\newcommand{\YourEmail}{[YourEmail]}

% Your state of residence
\newcommand{\YourState}{[YourState]}

% The client's name
\newcommand{\ClientName}{[ClientName]}

% The client's email
\newcommand{\ClientEmail}{[ClientEmail]}

% The city location of the client's headquarters
\newcommand{\ClientCity}{[ClientCity]}

% The state location of the client's headquarters
\newcommand{\ClientState}{[ClientState]}

% The event name
\newcommand{\EventName}{[EventName]}

% The session date (in 'Day of the Week', 'Month' 'Day Number', 'Year' format) (e.g., 'Wednesday, December 4, 1974')
\newcommand{\SessionDate}{[SessionDate]}
 
% The session time (in 'h:mm AM/PM' format)
\newcommand{\SessionTime}{[SessionTime]}

% The session total duration in minutes (numeric)
\newcommand{\SessionDurationNum}{[SessionDurationNum]}
 
% The session total duration in minutes (alpha)
\newcommand{\SessionDurationAlpha}{[SessionDurationAlpha]}
 
% The session presentation duration in minutes (numeric)
\newcommand{\PresentationDurationNum}{[PresentationDurationNum]}

% The session presentation duration in minutes (alpha)
\newcommand{\PresentationDurationAlpha}{[PresentationDurationAlpha]}
 
% The session Q&A duration in minutes (numeric)
\newcommand{\QnADurationNum}{[QnADurationNum]}

% The session Q&A duration in minutes (alpha)
\newcommand{\QnADurationAlpha}{[QnADurationAlpha}

% The venue name
\newcommand{\VenueName}{[VenueName]}

% The venue address
\newcommand{\VenueAddressLineOne}{[VenueAddress1]}
\newcommand{\VenueAddressAddressLineTwo}{[VenueAddress2]}

% The delivery date for specifications and completion date for the project
\newcommand{\DeliveryDate}{[date]}
\newcommand{\CompletionDate}{[date]}

% Payee's information
\newcommand{\PayeeName}{[Payee Name]}
\newcommand{\PaymentAddressLineOne}{[PaymentAddress1]}
\newcommand{\PaymentAddressLineTwo}{[PaymentAddress2]}
\newcommand{\PaymentAddressLineThree}{[PaymentAddress3]}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage}

\vspace*{\fill} % Add whitespace above to center the title page content

\begin{center}

{\LARGE Speaker Engagement Agreement for \ClientName's \EventName  ~Event}\\ [1.5cm]

Submitted: \today

\end{center}

\YourName\\

\AddressLineOne

\AddressLineTwo

\YourEmail

\vspace*{\fill} % Add whitespace below to center the title page content

\end{titlepage}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

This Speaker Engagement Agreement ("Agreement") is entered into as of \today ~(the "Effective Date") by and between \ClientName, LLC, a <type of company> company organized and existing under the laws of the State of \ClientState, ("Company" or "\ClientName"), and \YourName, an individual resident of the State of \YourState ~("Speaker"). Company and Speaker are collectively referred to as the "Parties". The Parties agree as follows:

%----------------------------------------------------------------------------------------
%	OVERVIEW SECTION
%----------------------------------------------------------------------------------------

\section{Overview}

\subsection{Company}

\ClientName, ~is a <description of company>. Headquartered in \ClientCity, \ClientState, <more info from Company's website>.

\subsection{Speaker}

Speaker is \YourName.

\subsection{Engagement}

\ClientName, ~hereby engages Speaker to present at its annual \EventName ~event, as further described below, and Speaker hereby agrees to present at the \EventName ~event under the terms and conditions set forth below.

%----------------------------------------------------------------------------------------
%	SERVICES OF SPEAKER SECTION
%----------------------------------------------------------------------------------------

\section{Services of Speaker}

\subsection{Description of Presentation/Topic}

Speaker willl give a presentation at the \EventName ~event on the topic of \textbf{\TalkTitle}.

\subsection{Venue}

Speaker will present at the \VenueName, located at \VenueAddressLineOne, \VenueAddressAddressLineTwo.

\subsection{Date and Time}

Speaker will present on \SessionDate ~(the "Event Date") at approximately \SessionTime ~local time.

\subsection{Length}

The presentation will last for approximately \SessionDurationNum ~(\SessionDurationAlpha) minutes and Speaker will make herself/himself available immediately before and immediately after the presentation. Speaker's presentation will be approximately \PresentationDurationNum ~(\PresentationDurationAlpha) minutes in length; a question-and-answer session lasting approximately \QnADurationNum ~(\QnADurationAlpha) minutes will follow Speaker's presentation.


%----------------------------------------------------------------------------------------
%	COMPENSATION SECTION
%----------------------------------------------------------------------------------------

\section{Compensation}

\subsection{Speaker Fee}

Company agrees to pay Speaker a fee of \FullFee ~for Speaker's services. Company shall pay 50\% of the speaker fee (\HalfFee) no later than thirty (30) days before the Event Date. Company shall pay the remaining 50\% of the speaker fee (\HalfFee) no later than thirty (30) days following the Event Date. Speaker will provide Company with invoices for each half of the speaker fee at least fifteen (15) days before each payment is due. Payments will be made in the form of a check, to be made payable to \YourName.

\subsection{Travel}

Company will book and pay for certain travel arrangements for Speaker (e.g., airfare, lodging, etc.), with such arrangements to be mutually agreed upon by Speaker and Company. In addition, Company will reimburse Speaker for additional, reasonable travel expenses incurred (e.g., transportation, meals, etc.). Speaker shall submit an invoice and original receipts for any reimbursable travel expenses paid by Speaker no later than fifteen (15) days following the Event Date. Company shall pay Speaker for all reimbursable travel expenses no later than thirty (30) days following the Event Date.

\subsection{Taxes}

Company will not pay or withhold federal, state, or local income or other payroll taxes on behalf of Speaker. Speaker is solely responsible for the payment and reporting of all taxes, withholdings, and other obligations.

\subsection{Form W-9}

An IRS Form W-9, available at www.IRS.gov, must be completed by Speaker. No payments will be made by Company until a Form W-9 is received by Speaker.

%----------------------------------------------------------------------------------------
%	RELATIONSHIP OF THE PARTIES SECTION
%----------------------------------------------------------------------------------------

\section{Relationship of the Parties}

The Parties agree that this Agreement shall not be construed to create any association, partnership, joint venture, employer-employee, master-servant, or agency relationship between the Parties. Speaker is an independent contractor and not an employee or agent of Company. Speaker acknowledges and agrees that Company has no responsibility to provide insurance or other fringe benefits normally associated with employee status.

%----------------------------------------------------------------------------------------
%	PRESENTATION AND RELEASE SECTION
%----------------------------------------------------------------------------------------

\section{Presentation and Release}

\subsection{Permission to Broadcast and Record}

Speaker agrees that Company may live stream and record Speaker's \EventName ~presentation. The \EventName ~presentation may only be streamed on Company's internal network, and any replay of the \EventName ~presentation must be for Company's internal purposes only. Speaker hereby grants to Company an irrevocable, royalty-free, perpetual, non-exclusive license to use the recording for internal Company use and play.

\subsection{Permission to Photograph}

Speaker agrees that Company may take photographs before or after Speaker's \EventName ~presentation, and that Company may make and use such photographs, including images of Speaker, on Company's website. Speaker has the right to approve or disapprove the use of any photographs prior to any public display by Company on its website. Speaker's approval shall not be unreasonably withheld, and Company and Speaker agree to work together to review the photographs in a timely manner. Speaker thereby grants to Company an irrevocable, royalty-free, perpetual, non-exclusive license to use, display, publish, and exhibit the photographs on its website once approved by Speaker.

%----------------------------------------------------------------------------------------
%	TERMINATION SECTION
%----------------------------------------------------------------------------------------

\section{Termination}

\subsection{Mutual Termination}

This Agreement may be terminated at any time by mutual written consent of the Parties.

\subsection{Termination Without Liability}

Either party may cancel the engagement and terminate this Agreement without liability by giving the other party written notice thereof at least thirty (30) days prior to the Event Date.

\subsection{Termination by Company}

If Company terminates this Agreement less than thirty (30) days prior to the Event Date, Company's liability to Speaker shall be limited to 50\% (\HalfFee) of the speaker fee and any nonrefundable travel expenses.

\subsection{Termination by Speaker}

Speaker may terminate this Agreement less than thirty (30) days prior to the Event Date due to illness, disability, death, or other inability to perform. If Speaker terminates the Agreement pursuant to this provision, Company shall have no obligation to make any payments to Speaker and Speaker shall return any fees paid by Company. Company and Speaker may, but are not required to, attempt to reschedule the Speaker's presentation at a mutually acceptable future date.

\subsection{Force Majeure}

The Parties agree that either party may terminate this Agreement and both Parties will be released from any liability or damages herein if the terms of this Agreement cannot be fulfilled due to an Act of God or any other cause beyond the reasonable control of the Parties, including but not limited to, unavoidable travel interruptions, flood or other weather-related emergency or disaster, fire, work stoppages, or terrorism. If the event of a force majeure occurrence, Speaker shall return any fees paid by Company. The Parties may, but are not required to, work together in good faith to reschedule the \textbf{\TalkTitle} presentation in the event of a force majeure occurrence.


%----------------------------------------------------------------------------------------
%	CONFIDENTIALITY SECTION
%----------------------------------------------------------------------------------------

\section{Confidentiality}

The Parties agree to maintain the confidentiality of the terms and conditions contained in this Agreement.

%----------------------------------------------------------------------------------------
%	INDEMNIFICATION SECTION
%----------------------------------------------------------------------------------------

\section{Indemnification}

Speaker agrees to indemnify and hold harmless Company, its officers, agents, and employees from and against any injury, loss, damage, or other liability arising out of or relating to the services performed by Speaker or from any breach of this Agreement, except for injury, loss, damage, or other liability resulting directly from Company's willful negligence or misconduct.

%----------------------------------------------------------------------------------------
%	NOTICES SECTION
%----------------------------------------------------------------------------------------

\section{Notices}

Any notice or communication under this Agreement given by a Party to the other Party must be in writing and will be effective upon delivery as follows: (i) if to \ClientName, when sent via email to \textbf{\ClientEmail}, and (ii) if to Speaker, when sent via email to \textbf{\YourEmail}.

%----------------------------------------------------------------------------------------
%	WARRANTIES AND AUTHORITY TO EXECUTE SECTION
%----------------------------------------------------------------------------------------

\section{Warranties and Authority to Execute}

\subsection{Company's Warranty}

Company represents and warrants that it has the right, power, and authority to enter into this Agreement and that the execution of this Agreement by the representatives signing is authorized.

\subsection{Speaker's Warranty}

Speaker represents and warrants that he/she has the right, power, and authority to enter into this Agreement and that doing so does not and will not conflict with any other agreements to which Speaker is a party.

\subsection{Agent's Warranty}

If an agent is signing this Agreement on behalf of Speaker, the agent expressly represents and warrants that she/he is authorized to do so on behalf of Speaker and has the authority to bind Speaker to this Agreement.


%----------------------------------------------------------------------------------------
%	MISCELLANEOUS SECTION
%----------------------------------------------------------------------------------------

\section{Miscellaneous}

\subsection{Assignment}

Neither Party may assign or delegate its rights and obligations under this Agreement without the prior, written consent of the other Party. This Agreement shall bind and inure to the benefit of the Parties hereto and their successors and assigns.

\subsection{Governing Law and Jurisdiction}

This Agreement shall be construed and enforced in accordance with the laws of the State of \ClientState ~and may be enforced in any state or federal court of competent jurisdiction located in the State of \ClientState.

\subsection{Waiver}

Any failure to enforce any provision of this Agreement shall not constitute a waiver thereof or of any other provision.

\subsection{Amendment}

This Agreement may not be amended, nor any obligation waived, except by a writing signed by both Parties.

\subsection{Severability}

In the event any term of this Agreement is found by any court to be void or otherwise unenforceable, the remainder of this Agreement shall remain valid and enforceable as though such term were absent upon the date of its execution.

\subsection{Counterparts}

This Agreement may be executed in counterparts, and delivered to the other Party either physically or by electronic means, each of which shall constitute an original and all of which together shall constitute one and the same instrument.

\subsection{Entire Agreement}

This document contains the entire agreement and understanding between the Parties with respect to the subject matter hereof and supersedes any and all prior understandings and agreements relating hereto, whether oral or written.\\

\begin{center}
\textit{[Remainder of Page Intentionally Blank. Signatures on Following Page]}
\end{center}

\pagebreak


%----------------------------------------------------------------------------------------
%	SIGNATURE SECTION
%----------------------------------------------------------------------------------------

\section{Signatures}


The Parties hereto have duly executed this Agreement as of the date written below:

%------------------------------------------------

\subsection*{The Company} % Suppress section numbering with the *

\ClientName \\

\begin{tabular}{lp{10pt}l}
Signature: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Print Name: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Title: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Date: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
\end{tabular}

%------------------------------------------------

\subsection*{The Speaker} % Suppress section numbering with the *

\YourName \\

\begin{tabular}{ l p{10pt} l }
Signature: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Print Name: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Title: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
Date: && \hspace{0.5cm} \makebox[3in]{\hrulefill} \\ \\[3pt]
\end{tabular}

%----------------------------------------------------------------------------------------

\end{document}
